RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-05-29 README.Rmd
adds Data Accessibility section as requested before going to proofs

[![Build Status](https://api.travis-ci.org/ropensci/RNeXML.png)](https://travis-ci.org/ropensci/RNeXML)

@@

An R package for reading, writing, integrating and publishing data using the Ecological Metadata Language (EML) format.

* **Note:** This package is still in active development and not yet submitted to CRAN.  Functions and documentation may be incomplete and subject to change.  
* Maintainer: Carl Boettiger
* Authors: Carl Boettiger, Scott Chamberlain, Hilmar Lapp, Kseniia Shumelchyk, Rutger Vos
* License: BSD-3 
* [Issues](https://github.com/ropensci/RNeXML/issues): Bug reports, feature requests, and development discussion.

@@

```{r echo=FALSE}
library(knitr)
opts_knit$set(upload.fun = imgur_upload)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=FALSE)
```

@@

Once we have created the `meta` elements, we can pass them to our `nexml_write` function, along with definitions of the namespaces.

```{r}
  nexml_write(bird.orders, 
              file = "example.xml", 
              meta = list(history, modified, website), 
              namespaces = c(skos = "http://www.w3.org/2004/02/skos/core#",
                             foaf = "http://xmlns.com/foaf/0.1/"))

@@

Add taxonomic identifier metadata to the OTU elements:

```{r}
nex <- add_trees(bird.orders)
nex <- taxize_nexml(nex)
```

@@

```{r}
library(geiger)
fitContinuous(tree, traits[1])
fitDiscrete(tree, traits[2])
```

@@

>>>>

[![DOI](https://zenodo.org/badge/doi/10.5281/zenodo.13131.svg)](http://dx.doi.org/10.5281/zenodo.13131)
[![Build Status](https://api.travis-ci.org/ropensci/RNeXML.png)](https://travis-ci.org/ropensci/RNeXML)

@@

* Maintainer: Carl Boettiger
* Authors: Carl Boettiger, Scott Chamberlain, Hilmar Lapp, Kseniia Shumelchyk, Rutger Vos
* License: BSD-3 
* [Issues](https://github.com/ropensci/RNeXML/issues): Bug reports, feature requests, and development discussion.

@@

```{r compile-settings, include=FALSE}
## Set the paths for cache and figure
library(methods)
library(knitr)
opts_chunk$set(cache = 1)
basename <- gsub(".Rmd", "", knitr:::knit_concord$get('infile')) 
opts_chunk$set(fig.path = paste("figure/", basename, "-", sep=""),
               cache.path = paste("cache/", basename, "/", sep=""))

```{r echo=FALSE}
library(knitr)
opts_knit$set(upload.fun = imgur_upload)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, comment = NA, verbose = TRUE)
```

@@

For this kind of richer annotation, it is best to build up our NeXML object sequentially. Frist
we will add `bird.orders` phylogeny to a new phylogenetic object, and then we will add the metadata
elements created above to this object. Finally, we will write the object out as an XML file:

```{r}
  birds <- add_trees(bird.orders)
  birds <- add_meta(meta = list(history, modified, website),
                    namespaces = c(skos = "http://www.w3.org/2004/02/skos/core#",
                                   foaf = "http://xmlns.com/foaf/0.1/"),
                    nexml=birds)
  nexml_write(birds, 
              file = "example.xml")

@@

Add taxonomic identifier metadata to the OTU elements:
<!-- This block relies on a robust internet connection that can occassionally fail.  Also it's a bit slow, so don't run it. After all, this command is tested in the unit tests.-->

```{r eval=FALSE}
nex <- add_trees(bird.orders)
nex <- taxize_nexml(nex)
```

@@

```{r}
library(geiger)
fitContinuous(tree, traits[1], ncores=1)
fitDiscrete(tree, traits[2], ncores=1)
```

@@

-----

[![ropensci footer](http://ropensci.org/public_images/github_footer.png)](http://ropensci.org)

### 2015-05-29 manuscripts/manuscript.Rmd
adds Data Accessibility section as requested before going to proofs

This project was supported in part by the National Evolutionary
Synthesis Center (NESCent) (NSF #EF-0905606), and grants from the
National Science Foundation (DBI-1306697) and the Alfred P Sloan
Foundation (Grant 2013-6-22). `RNeXML` started as a project idea for
the Google Summer of Code(TM), and we thank Kseniia Shumelchyk for taking
the first steps to implement it. We are grateful to F. Michonneau for
helpful comments on an earlier version of this manuscript.

>>>>

This project was supported in part by the National Evolutionary
Synthesis Center (NESCent) (NSF #EF-0905606), and grants from the
National Science Foundation (DBI-1306697) and the Alfred P Sloan
Foundation (Grant 2013-6-22). `RNeXML` started as a project idea for
the Google Summer of Code(TM), and we thank Kseniia Shumelchyk for taking
the first steps to implement it. We are grateful to F. Michonneau for
helpful comments on an earlier version of this manuscript, and reviews
by Matthew Pennell, Associate Editor Richard FitzJohn, and an anonymous
reviewer. At their behest, the reviews of FitzJohn and Pennell can be found in this
project's GitHub page at [github.com/ropensci/RNeXML/issues/120](https://github.com/ropensci/RNeXML/issues/121) and [github.com/ropensci/RNeXML/issues/120](https://github.com/ropensci/RNeXML/issues/120), together with our replies and a record of our revisions.

## Data Accessibility

All software, scripts and data used in this paper can be found in the permanent 
data archive Zenodo under the digital object identifier
 doi:10.5281/zenodo.13131 [@zenodo]. This DOI corresponds to a snapshot of the GitHub repository
at [github.com/ropensci/RNeXML](https://github.com/ropensci/RNeXML).
